\large \textbf{Leveraging Historical Ties between Cognitive Science and Computer Science to Guide Innovative Use of Computers in Education}

### 2016-02-01 paper.tex
removed unused and error-generating keywords from biblatex line

% sorting=none will order citations in order of appearance
% use sorting=nyt to sort by name, year, title
\usepackage[numbers, backend=biber,autolang=hyphen, bibencoding=inputenc, strict, isbn=false, uniquename=false, sorting=none, sortcites=true, style=numeric, autocite=superscript, url=false]{biblatex} % biblatex setup
\DeclareLanguageMapping{american}{american-apa}
\appto{\bibfont}{\footnotesize} % for 10pt bibliography
%\usepackage{xunicode}
\usepackage[american]{babel}
\usepackage[babel]{csquotes}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows,shapes,fit}
\usepackage{standalone}
\usepackage{mdframed}
\usepackage{capt-of}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage[parfill]{parskip}

@@

\let\textcite=\autocite
\addbibresource{../../computing.bib}

>>>>

% sorting=none will order citations in order of appearance
% use sorting=nyt to sort by name, year, title
\usepackage[backend=biber,autolang=hyphen, bibencoding=inputenc, isbn=false, uniquename=false, sorting=none, sortcites=true, style=numeric, autocite=superscript, url=false]{biblatex} % biblatex setup
\DeclareLanguageMapping{american}{american-apa}
\appto{\bibfont}{\footnotesize} % for 10pt bibliography
%\usepackage{xunicode}
\usepackage[american]{babel}
\usepackage[babel]{csquotes}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows,shapes,fit}
\usepackage{standalone}
\usepackage{mdframed}
\usepackage{capt-of}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage[parfill]{parskip}

@@

\let\textcite=\autocite
\addbibresource{computing.bib}
